%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Alexander}{Murray}
       {Electrical Technician}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    Passwangstrasse 57
    4059 Basel
    Switzerland
    ~
    \href{mailto:alex.murray@gmx.ch}{alex.murray@gmx.ch}
    \href{https://github.com/TheComet}{github.com/TheComet}
    \href{tel:41796884760}{+41 79 688 47 60}
  \section{languages}
    English/German
  \section{programming}
    C89/99
    C++ 
    CMake \& Gradle
    Python
    Java
    MATLAB \& Simulink
    GLSL \& HLSL
    VHDL
\end{aside}

\section{Summary}

\section{Experience}

\begin{entrylist}
  \entry
    {06-09 2016}
    {Ultrabox Previewer}
    {Summer Job, E+H Flowtec AG}
    {\emph{Developed a measurement data visualization and processing tool for ultrasonic flowmeters}}
\end{entrylist}

\section{Hobby Projects}

\begin{entrylist}
  \entry
    {}
    {Symbolic SFG solver \& visualizer}
    {}
    {\url{https://github.com/thecomet/tfp}}
  \entry
    {}
    {Inverse Kinematics solver library}
    {}
    {\url{https://github.com/thecomet/ik}}
  \entry
    {}
    {3D acoustic wave simulator for real-time sound propagation}
    {}
    {\url{https://github.com/TheComet/wavesim}}
  \entry
    {}
    {Various contributions to open source projects}
    {}
    {\url{https://github.com/thecomet}}
\end{entrylist}

\section{Skills}

\subsection{Hardware}
\begin{itemize}
    \item Large scale hardware manufacturing experience including the usage of pick\&place machines, reflow and wave soldering machines and their thermal profiles,  In-Circuit Testing (ICT) systems, repair of manufacturing errors, and various other production steps.
    \item Class 2 IPC-A-610 (?) certificate.
    \item Attended an ESD training seminar for correct handling of ESD sensitive components.
    \item Can systematically debug and repair hardware using standard equipment (oscilloscopes, multimeters, scalpel, soldering iron).
    \item Knowledge of mixed-signal, high-frequency, and low-noise layout considerations in PCB designs.
\end{itemize}

\subsection{Programming}
\begin{itemize}
    \item 6 years of experience developing, testing and maintaining C and C++ software in both a Windows and Linux environment using IDEs such as VSCode, Visual Studio, KDevelop, QtCreator and CLion.
    \item Experience writing and maintaining complex build systems (CMake, Premake, Makefiles) for automatically configuring, compiling, testing and deploying C and C++ applications. Experience with configuring continuous integration systems such as Buildbot and Travis CI.
    \item Ability to profile for performance and optimise critical sections of C/C++ code.
    \item Ability to use tools such as valgrind to detect and repair memory leaks or race conditions in threaded applications.
    \item Experience in writing automated unit tests to prove the correct implementation of algorithms and reduce development time.
    \item Experience in porting and using real-time operating systems such as FreeRTOS in embedded applications.
    \item Experience with the C Python API and writing Python bindings for performance critical code.
    \item Experience developing cross platform GUI applications using frameworks such as Qt, wxWidgets and WPF for C++ or Swing and JavaFX for Java.
    \item Extensive knowledge in development of 3D applications using OpenGL and higher level frameworks such as Ogre3D and Urho3D.
    \item Knowledge in writing GPU accelerated programs in GLSL and HLSL.
    \item Can write python scripts to automate redundant tasks and improve work efficiency
\end{itemize}

\subsection{Software}
\begin{itemize}
    \item 6 years of experience designing and routing circuits with Altium and Zuken CR-5000. Some experience with Eagle and KiCad.
    \item Experienced in using MATLAB and Simulink as well as open source alternatives such as Octave, Spyder and Jupyter.
    \item 6 years of experience with simulation software such as PSpice and LTspice.
    \item Familiar with MS Office tools Word, Excel, Power Point and Project, familiar with OpenOffice/LibreOffce and LaTeX.
    \item Some experience in RF filter design and simulation using Microwave Office and CST Microwave Studio.
\end{itemize}

\subsection{GNU/Linux}
\begin{itemize}
    \item 8 years experience using Linux based operating systems in both a hobbyist and production environment.
    \item Familiar with kernel rebuilding and compiling software from source.
    \item Experienced in remote administration of Linux based systems and troubleshooting.
    \item Acquainted with Gentoo, Ubuntu and Debian based Linux distributions.
\end{itemize}

\section{Education}

\begin{entrylist}
  \entry
    {2014-}
    {Bachelors in Electrical Engineering}
    {FHNW, Windisch}
    {\emph{Low-cost and low-power ultrasonic flow measurement system}}
  \entry
    {2009-2013}
    {Vocational School}
    {Berufsmaturit\"atsschule, AGS Basel}
    {}
  \entry
    {2009-2013}
    {Electronics Apprenticeship}
    {Endress + Hauser Flowtec AG, AGS Basel}
    {\emph{Graduated in the top 1\%. Developed a high voltage, high frequency output stage and a 16x16 RGB LED matrix.}}
  \entry
    {2007-2009}
    {Secondary School}
    {Sekundarschule Frenke, Liestal}
    {}
  \entry
    {2005-2007}
    {Primary School}
    {Sappeten, Bubendorf \& Schule Ramlinsburg}
    {}
\end{entrylist}

\end{document}

